Ensemble Stability of Biological Networks

### 2014-09-22 paper.tex
add todos regarding the definition of graph edit distance and hierarchy

@@

>>>>

\todo{add definition of graph edit distance to the most hierarchical network and define this as our measure of hierarchy}

@@

\todo{add description of \ref{fig:scc}D and \ref{fig:scc}F referring to the monotonic correlation between the upper bound of robustness and degree of hierarchy as defined by graph edit distance in a preceeding section}
